A multi-dimensional extension of the Lightweight Temporal Compression method

### 2018-10-10 paper.tex
Finished section III

% packages
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algorithmicx} % Doc is at http://tug.ctan.org/macros/latex/contrib/algorithmicx/algorithmicx.pdf
\usepackage{algpseudocode}
%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
%\renewcommand{\algorithmicensure}{\textbf{Output:}}
%\usepackage{algpseudocode}
\usepackage{amsfonts} % for R symbol (the set of real numbers)
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black,filecolor=black,urlcolor=blue}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{stmaryrd} % for llbracket and rrbracket
\usepackage{subcaption}
\usepackage{nicefrac}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{amsthm}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

@@

@@

\begin{abstract}
\end{abstract}

@@

LTC is among the stream compression method that provides the highest 
compression rate for the lowest resource (CPU, RAM) consumption. As 
such, it makes it a very good candidate for the compression of data 
streams acquired in embedded, low-power systems such as connected 
objects, systems on module (SoMs), etc The type of data acquired on 
such systems, however, is often multi-dimensional. For instance 
accelerometers and gyroscopes usually measure variables along 3 
directions, these variables being distinct but related through the 
actual movement of the sensor. In this paper, we investigate the 
extension of LTC to higher dimensions. First, we express the algorithm 
in an arbitrary vectorial space of dimension $n$. Second, we 
instantiate it for the Euclidean and xxx distances, in spaces of 
dimension 2D+t and 3D+t. Finally, we compare the multi-dimensional LTC 
to the 1-dimensional version, on gyroscopic data acquired on a SoM 
device.

In practice, It's needed to transmit raw data which has 
multi-parameters to clients e.g. Accelerometer, Euler Angle and 
Magnetometer etc. LTC not work well when we transmit multi-parameters 
data, cause if we just implement LTC for each parameter, the difference 
between estimation and origin could exceed error margin which was set 
in advance. For instance, there is a data $(x, y)$ with two parameters, 
and using LTC for both parameter respectively. According to LTC method 
$\mid{\hat{x}-x}\mid\leqslant \epsilon$~\cite{jalaleddine1990ecg}, the 
estimation may be $(\hat{x}=x+\epsilon, \hat{y}=y+\epsilon)$, then the 
difference between estimation and original data $(x,y)$ is which is 
bigger than error margin predefined. In this case, we design a new 
algorithm, which is multi-parameter version of LTC, and it also work 
with any type of distance. In standard LTC method, it checks if there 
is overlapping part between new sector area and recorded range. 
However, in our multidimensional method, we will map every data point 
into same time-stamp e.g. $t_0$. It is convenient for us to calculate 
distance between them and check if overlapping range exists. we provide 
Multidimensional-LTC with Euclidean and Manhattan distance in below.

@@

\section{Lightweight Temporal Compression}

Lightweight Temporal Compression 
(LTC~\cite{schoellhammer2004lightweight}) approximates the data stream 
by a piece-wise linear function of time, ensuring that the error at 
every time-point is bounded.

@@

The algorithm \emph{receives} a stream of \emph{data points} $x_i$
at times $t_i$ ($i \in \mathbb{N}$), and it \emph{transmits} a stream of data points $\xi_i$ 
at times $\tau_i$ ($i \in \mathbb{N}$). To simplify the notations, we assume that:
\begin{equation*}
\forall k \in \mathbb{N}, \  \exists ! i \in \mathbb{N} \  \tau_k = t_i
\end{equation*}
That is, transmission times coincide with reception times. 
We define the \emph{centered received points} as follows:
\begin{equation*}
\forall k \in \mathbb{N}\ , \forall j \in \mathbb{N^*},\ (u^k_j, y^k_j) = (t_{i+j}, x_{i+j}), \quad \mathrm{where\ }i\mathrm{\ is\ s.t.}\ t_i = \tau_k.
\end{equation*}
and:
\begin{equation*}
\forall k \in \mathbb{N},\  (u^k_0, y^k_0) = (\tau_k, \xi_k).
\end{equation*}
This definition is such that $u^k_0=0$, and $y^k_j$ is the $j^{th}$ data point received
after the $k^{th}$ transmission.

Figure~\ref{fig:ltc} illustrates the notations and algorithm.  
\begin{figure}
\includegraphics[width=\columnwidth]{ltc.pdf}
\caption{Illustration of the LTC algorithm and notations used. Red dots indicate transmitted points. Dashed lines
represent the high line and the low line before a point is transmitted.}
\label{fig:ltc}
\end{figure}
\subsection{LTC algorithm}

The LTC algorithm maintains two lines, the \emph{high line}, and the 
\emph{low line} defined by (1) the latest transmitted point and (2) the 
\emph{high point} (high line) and the \emph{low point} (low line). When 
a point ($t_i$, $x_i$) is received, the high line is updated as 
follows: if $x_i+\epsilon$ is below the high line, the high line is 
updated to the line defined by the last transmitted point and ($t_i$, 
$x_i$); otherwise, the high line is not updated. Likewise, the low line 
is updated from $x_i-\epsilon$. Threfore, any line located between the 
high line and the low line approximates the data points received since 
the last transmitted point with an error bounded by $\epsilon$.

Using the notations defined previously, the original LTC algorithm can 
be written as in Algorithm~\ref{algo:ltc}. For readability, we assume 
that access to data points is blocking, i.e., the program will wait 
until the points are available. We also assume that the content of 
variable \texttt{tr} is transmitted after each assignment of this 
variable. Function \texttt{line}, omitted for brevity, returns the 
ordinate at abscissa $x$ (1st argument) of the line defined by the points
in its 2nd and 3rd arguments.

\begin{algorithm}
\begin{algorithmic}[1]
\State tr = $(u^0_0, y^0_0)$ \Comment{last transmitted point}
\State k = 1 ; j = 1
\State lp = $y^1_1 - \epsilon$ \Comment{low point}
\State hp = $y^1_1 + \epsilon$ \Comment{high point}
%\Function{line}{$x$, ($x_0$, $y_0$), ($x_1$, $y_1$)} 
% \Comment{Return the ordinate of the line defined by $(x_0, y_0)$, $(x_1, y_1)$ at abscissa $x$.}
%\Return $y_0 + \frac{y_1-y_0}{x_1-x_0}(x-x_0)$
%\EndFunction
\While{True} \Comment{Process received points as they come}
    \State j += 1
    \State new\_lp = max($y^k_j-\epsilon$, line($u^k_j$, tr, ($u^k_{j-1}$, lp)))
    \State new\_hp = max($y^k_j+\epsilon$, line($u^k_j$, tr, ($u^k_{j-1}$, hp)))
    \If{new\_lp $<$ new\_hp} \Comment{Keep compressing}
        \State lp = new\_lp
        \State hp = new\_hp
        \State \textbf{continue}
    \EndIf
    \State tr = $(u^k_j, (lp+hp)/2)$
    \Comment{Transmit point}
    \State lp = $y^k_j-\epsilon$
    \State hp = $y^k_j+\epsilon$
    \State k += 1
    \State j = 0
\EndWhile
\end{algorithmic}
\caption{Original LTC algorithm, adapted from~\cite{schoellhammer2004lightweight}.}
\label{algo:ltc}
\end{algorithm}

@@

\section{Extension to dimension $n$}

In this section we provide a distance-independent formulation of LTC in 
dimension $n$. By $n$, we refer to the dimension of the data points 
($x_i$). To handle time, LTC actually operates in dimension 
$n+1$.

@@

The formulation of LTC in~\cite{schoellhammer2004lightweight} relies on 
the intersection of \emph{convex cones} in dimension $n+1$. For $n=1$, it 
corresponds to the intersection of triangles, which can efficiently be 
computed by maintaining boundary lines, as detailed in the previous 
section. In higher dimension, however, cone intersections are not so 
straighforward, due to the fact that the intersection between 2 cones 
may not be a cone.

To address this issue, we formulate LTC as an intersection test between 
\emph{balls} of dimension $n$, that is, segments for $n=1$, disks for 
$n=2$, etc. Balls are defined with respect to the \emph{norm} used in 
the vector space of data points. For $n=1$, the choice of the norm does 
not really matter, as all p-norms and the infinity norm are identical. 
In dimension $n$, however, norm selection will be critical.

@@

Let $(u_0^k, y_0^k) \in \mathbb{R}^{n+1}$ be the latest transmitted point. For convenience, all the subsequent points will be 
expressed in the orthogonal space with origin $(u_0^k, y_0^k)$. We denote by $(v_j, z_j)_{j \in \llbracket 0, m \rrbracket}$ such points:
\begin{equation*}
\forall j \leq m,\  (v_j, z_j) = (u_j^k - u_0^k, y_j^k - y_0^k)
\end{equation*}
Without loss of 
generality, we assume that the data points are sampled uniformly with a 
sampling period of 1 time unit.

We define $\mathcal{B}_j$ as the ball of $\mathbb{R}^n$ of center $z_j$ and of radius 
$\epsilon$:
\begin{equation*}
\mathcal{B}_j = \left\{ z \in \mathbb{R}^n,\  \norm{z-z_j} \leq \epsilon \right\} \ (j \leq m)
\end{equation*}
We define $\mathcal{B}'_j$ by plunging $\mathcal{B}_j$ in $\mathbb{R}^{n+1}$:
\begin{equation*}
\mathcal{B'}_j = \left\{ (a_0, \ldots, a_{n}) \in \mathbb{R}^{n+1},\  a_0 = v_j^k \mathrm{\ and\ } (a_1, \ldots, a_{n}) \in \mathcal{B}_j \right\}
\end{equation*}
$\mathcal{B'}_j$ defines a convex cone $\mathcal{C}_j$ in $\mathbb{R}^{n+1}$:
\begin{equation*}
\mathcal{C}_j = \left\{ \alpha x  \in \mathbb{R}^{n+1},\ x \in \mathcal{B'}_j,\ \alpha \in \mathbb{R}^+ \right\}
\end{equation*}

No data point will be transmitted as long as:
\begin{equation*}
\bigcap_{j=0}^m{\mathcal{C}_j} \neq \O
\end{equation*}
Which, due to the definition of convex cones, implies that:
\begin{equation*}
\exists x=(a_0, \ldots a_n) \in \mathbb{R}^{n+1},\ \forall j \in \llbracket 0, m \rrbracket,\ \forall \alpha \in \mathbb{R^+}, \alpha x \in \mathcal{C}_j
\end{equation*}
Without loss of generality, we can assume that $a_0=v^k_1$ since any multiple
of $x$ is also in $\mathcal{C}_j$. 
This implies that $x \in \mathcal{B}'_1$.

@@

It should be noted that the norm has a critical impact on the 
compression error and ratio. For instance, using the infinity instead 
of the Euclidean norm increases the compression error by a factor of 
$\sqrt{n}$ in dimension $n$, and increases the compression ratio by xxx.

%~ Point $k+1$ will be compressed if and only if:
%~ \begin{eqnarray*}
%~ && \bigcap_{i=1}^{k+1} {\mathcal{B}}_i \neq \O \\
%~ \Leftrightarrow && {\mathcal{B}}_{k+1} \cap \bigcap_{i=1}^{k} {\mathcal{B}}_i \neq \O
%~ \end{eqnarray*}

@@

At first, let us solve the \textit{n} disks intersect. We use a algorithm which is based on plane sweep and dichotomy. Assume a disk include center$(x,y)$ and radius $r$. The pseudo-code in Algorithm 1.
\begin{algorithm}
    \caption{whether disks intersect}
    \begin{flushleft}
        \textbf{Input:} $l$ - list of disks, $d$ - mapped coming disk, $p$ - point will be base point\\
        \textbf{Output:} $true|false$  is there a intersection\\ 
        \textbf{function} isIntersect$(l, d, p)$
    \end{flushleft}
    \begin{algorithmic}[1]
        \STATE $tmp_list \gets null$
        \STATE $max\_x\gets d.x+d.r$
        \STATE $min\_x\gets d.x-d.r$

        \FORALL{$old\_disk$ \textbf{in} $l$}
            \IF{$d \cap old\_disk = \emptyset$} % distance(d.center, old\_disk.center) > d.r + old\_disk.r
                \STATE \textbf{return} false
            \ELSIF{$d \cap old\_disk \neq d$}
                \STATE {$\textbf{add } old\_disk \textbf{ into } tmp\_list$\\
                        $max\_x\gets $ MIN($max\_x, old\_disk.x+old\_disk.r$)\\
                        $min\_x\gets $ MAX($min\_x, old\_disk.x-old\_disk.r$)}
            \ENDIF
        \ENDFOR
        \STATE $\textbf{add } d \textbf{ into } tmp\_list$
        \IF{$max\_x < min\_x$}
            \STATE \textbf{return} false
        \ENDIF
        \WHILE{$min\_x \leqslant max\_x$}
            \STATE $mid \gets (min\_x + max\_x)/2$
            \STATE $max\_y \gets +\infty$
            \STATE $min\_y \gets -\infty$
            \FOR{$i=1$ \textbf{to} $tmp\_list.length$}
                \STATE $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $x=mid$, $(P1.y\geqslant P2.y)$
                \IF{$P_1.y < max\_y$}
                    \STATE $max\_y \gets p_1.y$
                    \STATE $max\_index \gets i$
                \ENDIF
                \IF{$P_2.y > min\_y$}
                    \STATE $min\_y \gets p_2.y$
                    \STATE $min\_index \gets i$
                \ENDIF
            \ENDFOR
            \IF{$max\_y >= min\_y$}
                \STATE $p.x \gets mid$
                \STATE $p.y \gets (max\_y+min\_y)/2$
                \STATE $l \gets tmp\_list$
                \STATE \textbf{return} true
            \ENDIF
            \STATE {Assume $P_d$ is the intersection between line of 
            centers from $tmp\_list[max\_index]$ and $tmp\_list[min\_index]$
            , and their common chord}
            \IF{$P_d.x < mid$}
                \STATE $max\_y \gets mid-1$
            \ELSIF{$P_d.x > mid$}
                \STATE $min\_y \gets mid+1$
            \ENDIF
        \ENDWHILE
        \RETURN false
    \end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
    \caption{whether intersect  for n dimension}
    \begin{flushleft}
        \textbf{Input:} $l$ - list object, $o$ - object of mapped coming data, $p$ - point will be base point\\
        \textbf{Output:} $true|false$  is there a intersection\\
        \textbf{function} isIntersect$(l, o, p)$
    \end{flushleft}
    \begin{algorithmic}[1]
        \STATE $tmp_list \gets null$
        \STATE $max \gets o.d\_n+o.r$
        \STATE $min \gets o.d\_n-o.r$

        \FORALL{$old\_obj$ \textbf{in} $l$}
            \IF{$o \cap old\_obj = \emptyset$} 
                \STATE \textbf{return} false
            \ELSIF{$o \cap old\_obj \neq o$}
                \STATE {$\textbf{add } old\_obj \textbf{ into } tmp\_list$\\
                        $max\gets $ MIN($max, old\_obj.d\_n+old\_obj.r$)\\
                        $min\gets $ MAX($min, old\_obj.d\_n-old\_obj.r$)}
            \ENDIF
        \ENDFOR
        \STATE $\textbf{add } o \textbf{ into } tmp\_list$
        \IF{$max < min$}
            \STATE \textbf{return} false
        \ENDIF
        $p\_cp \gets p$
        \IF{Recursive$(min, max, n, p\_cp)$}
            \STATE $p \gets p\_cp$
            \STATE \textbf{return} true
        \ELSE
            \STATE \textbf{return} false
        \ENDIF
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}
    \begin{flushleft}
        \textbf{function} Recursive$(left, right, j, p)$  -- $j$ means $j_th$ dimension
    \end{flushleft}
    \begin{algorithmic}[1]
        \WHILE{$left \leqslant right$}
            \STATE $mid \gets (left + right)/2$
            \STATE $max \gets +\infty$
            \STATE $min \gets -\infty$
            \FOR{$i=1$ \textbf{to} $tmp\_list.length$}
                \STATE $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $d_{j}=mid$, $(P1.d_{j-1}\geqslant P2.d_{j-1})$
                \IF{$P_1.d_{j-1} < max$}
                    \STATE $max \gets p_1.d_{j-1}$
                    \STATE $max\_index \gets i$
                \ENDIF
                \IF{$P_2.d_{j-1} > min$}
                    \STATE $min \gets p_2.d_{j-1}$
                    \STATE $min\_index \gets i$
                \ENDIF
            \ENDFOR
            \IF{$max >= min$}
                \STATE $p.d_j \gets mid$
                \IF{Recursive$(min, max, j-1, p)$}
                    \STATE \textbf{return} true
                \ENDIF
            \ENDIF
            \STATE Assume $P_d$ is the intersection between common chord of two objects $tmp\_list[max\_index]$, $tmp\_list[min\_index]$ and their line of centers.
            \IF{$P_d.d_j < mid$}
                \STATE $right \gets mid-1$
            \ELSIF{$P_d.d_j > mid$}
                \STATE $left \gets mid+1$
            \ENDIF

        \ENDWHILE
        \RETURN false
    \end{algorithmic}
\end{algorithm}

>>>>

% packages
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algorithmicx} % Doc is at http://tug.ctan.org/macros/latex/contrib/algorithmicx/algorithmicx.pdf
\usepackage{algpseudocode}
%\newtheorem*{theorem}{Lemma}

%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
%\renewcommand{\algorithmicensure}{\textbf{Output:}}
%\usepackage{algpseudocode}
\usepackage{amsfonts} % for R symbol (the set of real numbers)
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black,filecolor=black,urlcolor=blue}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{stmaryrd} % for llbracket and rrbracket
\usepackage{subcaption}
\usepackage{nicefrac}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{amsthm}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

@@

\newtheorem*{theorem}{Theorem}

@@

\begin{abstract}
Lightweight Temporal Compression 
(LTC~\cite{schoellhammer2004lightweight}) is among the stream 
compression method that provides the highest compression rate for the 
lowest resource (CPU, RAM) consumption. As such, it makes it a very 
good candidate for the compression of data streams acquired in 
embedded, low-power systems such as connected 
objects, systems on module (SoMs), etc The type of data acquired on 
such systems, however, is often multi-dimensional. For instance 
accelerometers and gyroscopes usually measure variables along 3 
directions, these variables being distinct but related through the 
actual movement of the sensor. In this paper, we investigate the 
extension of LTC to higher dimensions. First, we provide a formulation of the algorithm 
in an arbitrary vectorial space of dimension $n$. Furthermore, we 
implement the algorithm for the infinity and Euclidean norms, in spaces of 
dimension 2D+t and 3D+t. Finally, we compare the multi-dimensional LTC 
to the 1-dimensional version, on gyroscopic data acquired on a SoM 
device.
\end{abstract}

@@

Section~\ref{sec:ltc} provides some background on the LTC algorithm. 
Section~\ref{sec:extension} presents our formulation in dimension $n$.

@@

\section{Lightweight Temporal Compression}
\label{sec:ltc}

LTC approximates the data stream 
by a piece-wise linear function of time, ensuring that the error at 
every time-point is bounded.

@@

The algorithm \emph{receives} a stream of \emph{data points} $x_i$
at times $t_i$ ($i \in \mathbb{N}$), and it \emph{transmits} a stream of data points $\xi_i$ 
at times $\tau_i$ ($i \in \mathbb{N}$). To simplify the notations, we assume that:
\begin{equation*}
\forall k \in \mathbb{N}, \  \exists ! i \in \mathbb{N} \  \tau_k = t_i
\end{equation*}
That is, transmission times coincide with reception times. 
We define the \emph{centered received points} as follows:
\begin{equation*}
\forall k \in \mathbb{N}\ , \forall j \in \mathbb{N^*},\ (u^k_j, y^k_j) = (t_{i+j}, x_{i+j}), \quad \mathrm{where\ }i\mathrm{\ is\ s.t.}\ t_i = \tau_k.
\end{equation*}
and:
\begin{equation*}
\forall k \in \mathbb{N},\  (u^k_0, y^k_0) = (\tau_k, \xi_k).
\end{equation*}
This definition is such that $y^k_j$ is the $j^{th}$ data point received
after the $k^{th}$ transmission.
Figure~\ref{fig:ltc} illustrates the notations and algorithm.  
\begin{figure}
\includegraphics[width=\columnwidth]{ltc.pdf}
\caption{Illustration of the LTC algorithm and notations used. Red dots indicate transmitted points. Dashed lines
represent the high line and the low line at times when a point is transmitted.}
\label{fig:ltc}
\end{figure}
\subsection{LTC algorithm}

The LTC algorithm maintains two lines, the \emph{high line}, and the 
\emph{low line} defined by (1) the latest transmitted point and (2) the 
\emph{high point} (high line) and the \emph{low point} (low line). When 
a point ($t_i$, $x_i$) is received, the high line is updated as 
follows: if $x_i+\epsilon$ is below the high line then the high line is 
updated to the line defined by the last transmitted point and ($t_i$, 
$x_i+\epsilon$); otherwise, the high line is not updated. Likewise, the low line 
is updated from $x_i-\epsilon$. Therefore, any line located between the 
high line and the low line approximates the data points received since 
the last transmitted point with an error bounded by $\epsilon$.

Using these notations, the original LTC algorithm can 
be written as in Algorithm~\ref{algo:ltc}. For readability, we assume 
that access to data points is blocking, i.e., the program will wait 
until the points are available. We also assume that the content of 
variable \texttt{tr} is transmitted after each assignment of this 
variable. Function \texttt{line}, omitted for brevity, returns the 
ordinate at abscissa $x$ (1st argument) of the line defined by the points
in its 2nd and 3rd arguments.

\begin{algorithm}
\begin{algorithmic}[1]
\State tr = $(u^0_0, y^0_0)$ \Comment{last transmitted point}
\State k = 0 ; j = 1
\State (lp, hp) = ($y^1_1 - \epsilon$, $y^1_1 + \epsilon$) \Comment{low and high points}

\While{True} \Comment{Process received points as they come}
    \State j += 1
    \State new\_lp = max($y^k_j-\epsilon$, line($u^k_j$, tr, ($u^k_{j-1}$, lp)))
    \State new\_hp = max($y^k_j+\epsilon$, line($u^k_j$, tr, ($u^k_{j-1}$, hp)))
    \If{new\_lp $<$ new\_hp} \Comment{Keep compressing}
        \State (lp = new\_lp, new\_hp)
        \State \textbf{continue}
    \EndIf
    \State tr = $(u^k_j, (lp+hp)/2)$
    \Comment{Transmit point}
    \State (lp, hp) = ($y^k_j-\epsilon$, $y^k_j+\epsilon$)
    \State k += 1
    \State j = 0
\EndWhile
\end{algorithmic}
\caption{Original LTC algorithm, adapted from~\cite{schoellhammer2004lightweight}.}
\label{algo:ltc}
\end{algorithm}

@@

\section{Extension to dimension $n$}
\label{sec:extension}
In this section we provide a norm-independent formulation of LTC in 
dimension $n$. By $n$ we refer to the dimension of the data points 
$x_i$. To handle time, LTC actually operates in dimension 
$n+1$.

@@

We note that the formulation of LTC in~\cite{schoellhammer2004lightweight} relies on 
the intersection of \emph{convex cones} in dimension $n+1$. For $n=1$, it 
corresponds to the intersection of triangles, which can efficiently be 
computed by maintaining boundary lines, as detailed previously. In higher dimension, however, cone intersections are not so 
straighforward, due to the fact that the intersection between cones 
may not be a cone.

To address this issue, we formulate LTC as an intersection test between 
\emph{balls} of dimension $n$, that is, segments for $n=1$, disks for 
$n=2$, etc. Balls are defined from the \emph{norm} used in 
the vector space of data points. For $n=1$, the choice of the norm does 
not really matter, as all p-norms and the infinity norm are identical. 
In dimension $n$, however, norm selection will be critical.

@@

\subsubsection{Definitions}

Let $(u_0^k, y_0^k) \in \mathbb{R}^{n+1}$ be the latest transmitted point. For convenience, all the subsequent points will be 
expressed in the orthogonal space with origin $(\tau^k, \xi^k)$. We denote by $(v_j, z_j)_{j \in \llbracket 0, m \rrbracket}$ such points:
\begin{equation*}
\forall j \leq m,\  (v_j, z_j) = (u_j^k - \tau^k, y_j^k - \xi^k)
\end{equation*}
We define $\mathcal{B}_j$ as the ball of $\mathbb{R}^n$ of center $\frac{1}{j}z_j$ and of radius 
$\frac{\epsilon}{j}$:
\begin{equation*}
\mathcal{B}_j = \left\{ z \in \mathbb{R}^n,\  \norm{z-\frac{v_1}{v_j}z_j} \leq \frac{v_1}{v_j}\epsilon \right\}
\end{equation*}

\subsection{LTC property}

We formulate the \emph{LTC property} as follows:
\begin{equation*}
\exists z \in \mathbb{R}^n, \ \forall j \in \llbracket 1, m \rrbracket, \norm{\frac{v_j}{v_1}z-z_j} \leq \epsilon.
\end{equation*}
The LTC algorithm ensures that the LTC property is 
verified between each transmission. Indeed, all the data points 
$z$ such that $(v_1, z)$ is between the high line and the low line 
verify the property. Line 9 in Algorithm~\ref{algo:ltc} guarantees that
such a point exists.
The LTC property can be written as follows:
\begin{equation*}
\exists z \in \mathbb{R}^n, \ \forall j \in \llbracket 1, m \rrbracket, \norm{z-\frac{v_1}{v_j}z_j} \leq \frac{v_1}{v_j}\epsilon
\end{equation*}
that is:
\begin{equation}
\bigcap_{j=1}^m \mathcal{B}_j \neq \O
\label{eq:ltc-property}
\end{equation}
Note that $(\mathcal{B}_j)_{j \in \llbracket 1, m \rrbracket}$ is a sequence
of balls of strictly decreasing radius, since $v_j > v_1$.
\todo{Add a figure to illustrate this}

\subsection{Algorithm}

The LTC algorithm generalized to dimension $n$ test, for each data point,
that the LTC property in Equation~\ref{eq:ltc-property} is verified. It is written in
Algorithm~\ref{algo:general-ltc}.
\begin{algorithm}
\begin{algorithmic}[1]
\State tr = ($\tau, \xi$) = ($u^0_0, y^0_0$)
\State k = 0 ; j = 0
\While{True}
    \State j += 1
    \State ($v_j, z_j$) = ($u_j^k - \tau, y_j^k - \xi$)
    \If{$\bigcap_{l=1}^j{\mathcal{B}_l} \neq \O$}
        \State \textbf{continue}
    \EndIf
    \State Pick $z$ in $\bigcap_{l=1}^{j-1}{\mathcal{B}_j}$
    \State tr = ($\tau$, $\xi$) = ($u^k_{j-1}, z$)
    \State k += 1
    \State j = 0
\EndWhile
\end{algorithmic}
\caption{Generalized LTC}
\label{algo:general-ltc}
\end{algorithm}

\todo{Check algorithms (reimplement)}

\subsection{Ball intersections}

Although Algorithm~\ref{algo:general-ltc} looks simple, one should not 
overlook the fact that there is no good general algorithm to test 
whether a set of balls intersect. The best general algorithm we could find 
so far relies on Helly's theorem which is formulated as follows~\cite{helly1923mengen}:
\begin{theorem}
Let $\left\{ X_i \right\}_{i \in \llbracket 1, m \rrbracket}$ be a collection of convex subsets of $\mathbb{R}^n$. If the intersection of every $n+1$ 
subsets is non-empty, then the whole collection has an non-empty intersection.
\end{theorem}
This theorem leads to an algorithm of complexity ${m \choose n+1}$ which is 
not usable in resource-constrained environment.

The only feasible algorithm that we found is norm-specific. It 
maintains a representation of the intersection 
$\bigcap_{j=1}^{m}{\mathcal{B}_m}$ which is updated at every iteration.
The intersection tests can then be done in constant time, however, 
updating the representation of the intersection may be more costly 
depending on the norm used. For the infinity norm, the representation 
is a rectangular cuboid which is straightforward to update by 
intersection with an n-ball, since the n-ball is a rectangular cuboid too.
For the Euclidean norm, the representation is a volume with no specific property,
which is more costly to maintain.

@@

As mentioned before, norm selection in $\mathbb{R}^n$ has a critical 
impact on the compression error and ratio. To appreciate this effect, 
let us consider the comparison between the infinity norm and the 
Euclidean norm in dimension 2. By comparing the unit disk to the unit 
square, we obtain that the compression ratio of a random stream would 
be $\frac{4}{\pi}$ times larger with the infinity norm than with the 
Euclidean norm. Conversely, a compression error bounded by $\epsilon$ 
with the infinity norm corresponds to a compression error of 
$\frac{\epsilon}{\sqrt{2}}$ with the Euclidean norm. Unsurprisingly, the
infinity norm is more 'tolerant' than the Euclidean norm.

\todo{Perhaps add a figure}

It should also be noted that using the infinity norm boils down to the 
use of the 1D LTC algorithm independently in each dimension: a data 
point is transmitted as soon as the linear approximation doesn't hold 
in any of the coordinates. \todo{This is unclear}

@@

At first, let us solve the \textit{n} disks intersect. We use a algorithm which is based on plane sweep and dichotomy. Assume a disk include center$(x,y)$ and radius $r$. The pseudo-code in Algorithm 1.
\begin{algorithm}
    \caption{whether disks intersect}
    \begin{flushleft}
        \textbf{Input:} $l$ - list of disks, $d$ - mapped coming disk, $p$ - point will be base point\\
        \textbf{Output:} $true|false$  is there a intersection\\ 
        \textbf{function} isIntersect$(l, d, p)$
    \end{flushleft}
    \begin{algorithmic}[1]
        \State $tmp_list \gets null$
        \State $max\_x\gets d.x+d.r$
        \State $min\_x\gets d.x-d.r$

        \ForAll{$old\_disk$ \textbf{in} $l$}
            \If{$d \cap old\_disk = \emptyset$} % distance(d.center, old\_disk.center) > d.r + old\_disk.r
                \State \textbf{return} false
            \ElsIf{$d \cap old\_disk \neq d$}
                \State {$\textbf{add } old\_disk \textbf{ into } tmp\_list$\\
                        $max\_x\gets $ MIN($max\_x, old\_disk.x+old\_disk.r$)\\
                        $min\_x\gets $ MAX($min\_x, old\_disk.x-old\_disk.r$)}
            \EndIf
        \EndFor
        \State $\textbf{add } d \textbf{ into } tmp\_list$
        \If{$max\_x < min\_x$}
            \State \textbf{return} false
        \EndIf
        \While{$min\_x \leqslant max\_x$}
            \State $mid \gets (min\_x + max\_x)/2$
            \State $max\_y \gets +\infty$
            \State $min\_y \gets -\infty$
            \For{$i=1$ \textbf{to} $tmp\_list.length$}
                \State $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $x=mid$, $(P1.y\geqslant P2.y)$
                \If{$P_1.y < max\_y$}
                    \State $max\_y \gets p_1.y$
                    \State $max\_index \gets i$
                \EndIf
                \If{$P_2.y > min\_y$}
                    \State $min\_y \gets p_2.y$
                    \State $min\_index \gets i$
                \EndIf
            \EndFor
            \If{$max\_y >= min\_y$}
                \State $p.x \gets mid$
                \State $p.y \gets (max\_y+min\_y)/2$
                \State $l \gets tmp\_list$
                \State \textbf{return} true
            \EndIf
            \State {Assume $P_d$ is the intersection between line of 
            centers from $tmp\_list[max\_index]$ and $tmp\_list[min\_index]$
            , and their common chord}
            \If{$P_d.x < mid$}
                \State $max\_y \gets mid-1$
            \ElsIf{$P_d.x > mid$}
                \State $min\_y \gets mid+1$
            \EndIf
        \EndWhile
        \Return false
    \end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
    \caption{whether intersect  for n dimension}
    \begin{flushleft}
        \textbf{Input:} $l$ - list object, $o$ - object of mapped coming data, $p$ - point will be base point\\
        \textbf{Output:} $true|false$  is there a intersection\\
        \textbf{function} isIntersect$(l, o, p)$
    \end{flushleft}
    \begin{algorithmic}[1]
        \State $tmp_list \gets null$
        \State $max \gets o.d\_n+o.r$
        \State $min \gets o.d\_n-o.r$

        \ForAll{$old\_obj$ \textbf{in} $l$}
            \If{$o \cap old\_obj = \emptyset$} 
                \State \textbf{return} false
            \ElsIf{$o \cap old\_obj \neq o$}
                \State {$\textbf{add } old\_obj \textbf{ into } tmp\_list$\\
                        $max\gets $ MIN($max, old\_obj.d\_n+old\_obj.r$)\\
                        $min\gets $ MAX($min, old\_obj.d\_n-old\_obj.r$)}
            \EndIf
        \EndFor
        \State $\textbf{add } o \textbf{ into } tmp\_list$
        \If{$max < min$}
            \State \textbf{return} false
        \EndIf
        $p\_cp \gets p$
        \If{Recursive$(min, max, n, p\_cp)$}
            \State $p \gets p\_cp$
            \State \textbf{return} true
        \Else
            \State \textbf{return} false
        \EndIf
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}
    \begin{flushleft}
        \textbf{function} Recursive$(left, right, j, p)$  -- $j$ means $j_th$ dimension
    \end{flushleft}
    \begin{algorithmic}[1]
        \While{$left \leqslant right$}
            \State $mid \gets (left + right)/2$
            \State $max \gets +\infty$
            \State $min \gets -\infty$
            \For{$i=1$ \textbf{to} $tmp\_list.length$}
                \State $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $d_{j}=mid$, $(P1.d_{j-1}\geqslant P2.d_{j-1})$
                \If{$P_1.d_{j-1} < max$}
                    \State $max \gets p_1.d_{j-1}$
                    \State $max\_index \gets i$
                \EndIf
                \If{$P_2.d_{j-1} > min$}
                    \State $min \gets p_2.d_{j-1}$
                    \State $min\_index \gets i$
                \EndIf
            \EndFor
            \If{$max >= min$}
                \State $p.d_j \gets mid$
                \If{Recursive$(min, max, j-1, p)$}
                    \State \textbf{return} true
                \EndIf
            \EndIf
            \State Assume $P_d$ is the intersection between common chord of two objects $tmp\_list[max\_index]$, $tmp\_list[min\_index]$ and their line of centers.
            \If{$P_d.d_j < mid$}
                \State $right \gets mid-1$
            \ElsIf{$P_d.d_j > mid$}
                \State $left \gets mid+1$
            \EndIf

        \EndWhile
        \Return false
    \end{algorithmic}
\end{algorithm}
